Generating Random Logic Programs Using Constraint Programming

### 2020-01-18 paper/paper.tex
Generating some  data
Found an improvement to one of the constraints
A bit of writing

We also use Choco~4.10.2 \cite{choco}. This works with both Prolog
\cite{DBLP:books/daglib/0041598} and ProbLog \cite{DBLP:conf/ijcai/RaedtKT07}.
Tested with SWI-Prolog \cite{DBLP:journals/tplp/WielemakerSTL12}.

@@

\begin{constraint}
  For $i = 0, \dots, \maxNumNodes{} - 1$, if $\variable{numNodes} \le
  i$, then
  \[
    \variable{treeStructure}[i] = i \quad \text{and} \quad
    \variable{treeValues}[i].\variable{name} = \top,
  \]
  else
  \[
    \variable{treeStructure}[i] < \variable{numNodes}.
  \]
\end{constraint}

@@

\section{Eliminating Variable Symmetries} \label{sec:variable_symmetry}
% TODO: only if we have multiple variables

Given any clause, we can permute the variables in it without changing the
meaning of the clause or the entire program. Thus, we want to fix the order of
variables to eliminate unnecessary symmetries. Informally, we can say that
variable $X$ goes before variable $Y$ if its first occurrence in either the head
or the body of the clause is before the first occurrence of $Y$.

@@

\begin{constraint}[Redundant]
  For $u \ne v \in \constants{} \cup \variables{} \cup \{ \Box \}$,
  \[
    \variable{occurrences}[u] \cap \variable{occurrences}[v] = \emptyset.
  \]
\end{constraint}

@@

\begin{constraint}[Redundant]
  $\variable{allDifferentExcept0}(\variable{introductions})$.
\end{constraint}

@@

\begin{constraint}[Redundant]
  For $v \in \variables{}$,
  \[
    \variable{introductions}[v] \ne 0 \quad \implies \quad
    \variable{introductions}[v] - 1 \in \variable{occurrences}[v].
  \]
\end{constraint}

\subsection{A Redundant Constraint}

For each clause...

\begin{definition}
  We define an auxiliary set variable
  \[
    \variable{potentialIntroductions} \subseteq \{ 0, \dots, N \}
  \]
  by: for $i = 0, \dots, \maxNumNodes{} - 1$, if
  $\variable{treeValues}[i].\variable{name} \in \tokens{}$, then
  \[
    \variable{potentialIntroductions} \cap \{ \maxArity{} \times (i + 1) + j + 1
    \mid j = 0, \dots, \maxArity{} - 1 \} = \emptyset.
  \]
\end{definition} % TODO: maybe add to the example
In other words, if the node not a predicate, a variable cannot be introduced as
one of its `arguments'.

@@

\section{Interactions Between Clauses}

@@

\begin{definition}
  Let $\mathsf{P}$ be a predicate in a program $\mathscr{P}$. The
  \emph{dependencies} of $\mathsf{P}$ is the smallest set $D_{\mathsf{P}}$ such
  that:
  \begin{itemize}
  \item $\mathsf{P} \in D_{\mathsf{P}}$,
  \item for every $\mathsf{Q} \in D_{\mathsf{P}}$, the nodes with arrows to
    $\mathsf{Q}$ in $G_{\mathscr{P}}$ are all in $D_{\mathsf{P}}$.
  \end{itemize}
\end{definition}

@@

% TODO: example of edge positivity/negativity
% TODO: this is not a complete program (by my definition). Make it clear in the text.
\begin{example} \label{ex:program}
  Consider the following program:
  \begin{align}
    \mathsf{sibling}(X, Y) &\gets \mathsf{parent}(X, Z) \land \mathsf{parent}(Y, Z), \nonumber \\
    \mathsf{father}(X, Y) &\gets \mathsf{parent}(X, Y) \land \neg\mathsf{mother}(X, Y). \label{eq:example_clause}
  \end{align}
  Its predicate dependency graph is in \cref{fig:predicate_dependencies}.
  Because of the negation in \cref{eq:example_clause} (as seen in
  \cref{fig:example_tree2}), the edge from $\mathsf{mother}$ to
  $\mathsf{father}$ is negative, while the other two edges are positive.

@@

% TODO: continue writing from here
We define a \emph{dependency} as an algebraic data type that is either
determined (in which case it holds only the index of the \texttt{predicate}) or
undetermined (in which case it also holds the indices of the \texttt{source} and
\texttt{target} vertices, corresponding to the edge responsible for making the
dependency undetermined (exactly one, otherwise we don't consider the edge)).

@@

\begin{algorithm}[p]
  \SetKwFunction{getDependencies}{getDependencies}
  \SetKwFunction{isDetermined}{isDetermined}
  \SetKwFunction{fail}{fail}
  \SetKwFunction{removeValue}{removeValue}
  \SetKwData{predicate}{predicate}
  \SetKwData{source}{source}
  \SetKwData{target}{target}
  \KwData{predicates $p_1$, $p_2$; adjacency matrix $\mathbf{A}$}
  \For{$(d_1, d_2) \in \getDependencies{$p_1$, \logical{false}} \times
      \getDependencies{$p_2$, \logical{false}}$ such that $d_1.\predicate =
      d_2.\predicate$}{
    \lIf{$d_1$ {\bf is} $\Determined$ {\bf and} $d_2$ {\bf is}
      $\Determined$}{\fail{}}
    \If{$d_1$ {\bf is} $\Determined$ {\bf and} $d_2$ {\bf is}
      $\AlmostDetermined(\_, s, t)$ {\bf or} \hspace{50pt} $d_2$ {\bf is} $\Determined$ {\bf
        and} $d_1$ {\bf is} $\AlmostDetermined(\_, s, t)$}{
      $\mathbf{A}[s][t]$.\removeValue{$1$}\;
    }
  }
  \caption{Propagation algorithm for predicate independence}
\end{algorithm}

\begin{algorithm}[p]
  \SetKwFunction{getDependencies}{getDependencies}
  \SetKwFunction{isDetermined}{isDetermined}
  \SetKwData{predicate}{predicate}
  \KwData{predicates $p_1$, $p_2$}
  $D \gets \{ (d_1, d_2) \in \getDependencies{$p_1$, \logical{true}} \times
  \getDependencies{$p_2$, \logical{true}} \mid d_1.\predicate = d_2.\predicate
  \}$\;
  \lIf{$D = \emptyset$}{\Return{\textsc{true}}}
  \lIf{$\exists (\Determined \_, \Determined \_) \in D$}{\Return{\textsc{false}}}
  \Return{\textsc{undefined}}\;
  \caption{Entailment check for predicate independence}
  \label{alg:independence_entailment}
\end{algorithm}

% TODO: introduce this sum data type syntax
\begin{grammar}
  <dependency> ::= $\Determined p$ | $\Undetermined p$ | $\AlmostDetermined(p, s, t)$
\end{grammar}
where $p,s,t \in \predicates{}$. For a dependency $d$---regardless of its exact
type---we will refer to its predicate $p$ as $d.\variable{predicate}$.
% TODO: underscore represents a variable that can take any value (different
% underscores can take different values)

\begin{algorithm}[p]
  \SetKwData{edgeExists}{edgeExists}
  \SetKwData{predicate}{predicate}
  \SetKwData{source}{source}
  \SetKwData{target}{target}
  \SetKwData{all}{allDependencies}
  \SetKwFunction{isDetermined}{isDetermined}
  \SetKwFunction{getDependencies}{getDependencies}
  \SetKwProg{Fn}{Function}{:}{}
  \KwData{a $|\predicates{}| \times |\predicates{}|$ adjacency matrix
    $\mathbf{A}$ with $\{ 0, 1 \}$ as the domain}
  \Fn{\getDependencies{$p$, \all}} {
    $D \gets \{ \Determined p \}$\;
    \While{\logical{true}}{
      $D' \gets \emptyset$\;
      \For{$d \in D$ {\bf and} $q \in \predicates{}$}{
        $\edgeExists \gets \mathbf{A}[q][d.\predicate] = \{ 1 \}$\;
        \uIf{$\edgeExists$ {\bf and} $d$ {\bf is} $\Determined$}{
          $D' \gets D' \cup \{ \Determined q \}$
        }
        \uElseIf{$\edgeExists$ {\bf and} $d$ {\bf is} $\AlmostDetermined(\_, s, t)$}{
          $D' \gets D' \cup \{ \AlmostDetermined(q, s, t) \}$\;
        }
        \uElseIf{$|\mathbf{A}[q][d.\predicate]| > 1$ {\bf and} $d$ {\bf is}
          $\Determined r$}{
          $D' \gets D' \cup \{ \AlmostDetermined(q, q, r) \}$\;
        }
        \ElseIf{$|\mathbf{A}[q][d.\predicate]| > 1$ {\bf and} \all}{
          $D' \gets D' \cup \{ \Undetermined q \}$\;
        }
      }
      \lIf{$D' = D$}{\Return{$D$}}
      $D \gets D'$\;
    }
  }
  \caption{Computing the dependencies of a predicate}
\end{algorithm}
% TODO: any way to test all of this?

% TODO: Discuss that the algorithms work in case there are multiple 'paths'
% without any issues.
% TODO: An example of algorithms, showing a program that's not fully determined
% yet, a dependency graph (with dashed and grayed out edges). Create a situation
% with multiple different dependency paths such that propagation would result in
% a solution).

\begin{figure}[t]
  \centering
\end{figure}

\begin{figure}[t]
  \centering
  \begin{minipage}{.49\textwidth}
    \centering
    \[
      \begin{blockarray}{ccccccc}
        \begin{block}{ccc(cccc)}
          \mathsf{father} & & & 0 & 0 & 0 & 0 \\
          \mathsf{mother} & & & 1 & 0 & 0 & 0 \\
          \mathsf{parent} & & & 1 & \fbox{\{ 0, 1 \}} & \{ 0, 1 \} & \{ 0, 1 \} \\
          \mathsf{sibling} & & & 0 & 0 & 0 & 0 \\
        \end{block}
      \end{blockarray}
    \]
    \caption{The adjacency matrix defined using \cref{def:adjacency_matrix} for
      \cref{example:independence}}
    \label{fig:dependencies_matrix}
  \end{minipage}
  \begin{minipage}{.5\textwidth}
    \centering
    \begin{tikzpicture}
      \node[draw] (parent) at (0, 0.5) {$\mathsf{parent}$};
      \node[draw] (mother) at (0, -0.5) {$\mathsf{mother}$};
      \node[draw] (sibling) at (2, 0.5) {$\mathsf{sibling}$};
      \node[draw] (father) at (2, -0.5) {$\mathsf{father}$};
      \draw[-{Stealth}] (parent) edge (father);
      \draw[-{Stealth}] (mother) edge (father);
      \draw[-{Stealth},dashed,darkgray] (parent) edge (sibling);
      \draw[-{Stealth},dashed,darkgray] (parent) edge (mother);
    \end{tikzpicture}
    \caption{The predicate dependency graph that corresponds to
      \cref{fig:dependencies_matrix}. Dashed edges are undetermined---they may
      or may not exist.}
    \label{fig:dependencies2}
  \end{minipage}
\end{figure}
% TODO: make sure my definitions and examples are consistent with loops

@@

\section{Entailment Checking for Negative/All Cycles}
% TODO: explain that the hasNegativeCycles algorithm is an extension of a simple
% cycle detection algorithm.
% TODO: the difficulty with propagation is that there is no good way to define
% the adjacency matrix with 0/-1/+1 values, the negativity condition is too
% difficult.
% TODO: NB: the set of decision variables for this constraint must exclude all
% arguments.
% In order to avoid thrashing, we fix the following variable ordering: [...]. Example of thrashing: P(X, a) <- ~P(X, b) contradicts the negative cycle constrant. Let's try P(X, a) <- P(X, c) instead (and so on).

\begin{algorithm}[t]
  \KwData{a constraint model for a logic program $\mathscr{P}$ amid execution}
  \SetKwFunction{hasNegativeCycles}{hasNegativeCycles}
  Let $\mathscr{R} \subseteq \mathscr{P}$ be the largest subprogram of
  $\mathscr{P}$ with all bodies and all predicates in heads fully
  determined\footnotemark\;
  \lIf{$\mathscr{R} = \emptyset$}{\Return{\textsc{undefined}}}
  \lIf{\hasNegativeCycles($G_{\mathscr{R}}$)}{\Return{\textsc{false}}}
  \lIf{$\mathscr{R} = \mathscr{P}$}{\Return{\textsc{true}}}
  \Return{\textsc{undefined}}\;
  \caption{Entailment check for negative cycles}
\end{algorithm}
\footnotetext{Due to the definition of independence, the arguments of the head
  atom need not be determined.}

>>>>

We also use Choco~4.10.2 \cite{choco}. This works with both Prolog
\cite{DBLP:books/daglib/0041598} and ProbLog \cite{DBLP:conf/ijcai/RaedtKT07}.
%Tested with SWI-Prolog \cite{DBLP:journals/tplp/WielemakerSTL12}.

@@

\begin{constraint}
  For $i = 1, \dots, \maxNumNodes{} - 1$, if $i \ge \variable{numNodes}$, then
  \[
    \variable{treeStructure}[i] = i \quad \text{and} \quad
    \variable{treeValues}[i].\variable{name} = \top,
  \]
  else
  \[
    \variable{treeStructure}[i] < i.
  \]
\end{constraint}

@@

\section{Eliminating Variable Symmetries} \label{sec:variable_symmetry}

Given any clause, we can permute the variables in it without changing the
meaning of the clause or the entire program. Thus, we want to fix the order of
variables to eliminate unnecessary symmetries. Informally, we can say that
variable $X$ goes before variable $Y$ if its first occurrence in either the head
or the body of the clause is before the first occurrence of $Y$. Note that the
constrains described in this section only make sense if $|\variables| > 1$. Also
note that all definitions and constraints here are on a per-clause basis.

@@

@@

@@

\subsection{Redundant Constraints}

We add a number of redundant constraints to make search more efficient.

\begin{constraint}
  For $u \ne v \in \constants{} \cup \variables{} \cup \{ \Box \}$,
  \[
    \variable{occurrences}[u] \cap \variable{occurrences}[v] = \emptyset.
  \]
\end{constraint}

\begin{constraint}
  $\variable{allDifferentExcept0}(\variable{introductions})$.
\end{constraint}

\begin{constraint}
  For $v \in \variables{}$,
  \[
    \variable{introductions}[v] \ne 0 \quad \implies \quad
    \variable{introductions}[v] - 1 \in \variable{occurrences}[v].
  \]
\end{constraint}

\begin{definition}
  We define an auxiliary set variable
  \[
    \variable{potentialIntroductions} \subseteq \{ 0, \dots, N \}
  \]
  by: for $i = 0, \dots, \maxNumNodes{} - 1$, if
  $\variable{treeValues}[i].\variable{name} \not\in \predicates{}$, then
  \[
    \variable{potentialIntroductions} \cap \{ \maxArity{} \times (i + 1) + j + 1
    \mid j = 0, \dots, \maxArity{} - 1 \} = \emptyset.
  \]
\end{definition} % TODO: explain these numbers
In other words, if the node is not a predicate, a variable cannot be introduced
as one of its `arguments'.

@@

@@

\begin{definition}
  Let $\mathsf{P}$ be a predicate in a program $\mathscr{P}$. The set of
  \emph{dependencies} of $\mathsf{P}$ is the smallest set $D_{\mathsf{P}}$ such
  that:
  \begin{itemize}
  \item $\mathsf{P} \in D_{\mathsf{P}}$,
  \item for every $\mathsf{Q} \in D_{\mathsf{P}}$, all direct predecessors of
    $\mathsf{Q}$ in $G_{\mathscr{P}}$ are in $D_{\mathsf{P}}$.
  \end{itemize}
\end{definition}

@@

\begin{example} \label{ex:program}
  Consider the following (fragment of a) program:
  \begin{align}
    \mathsf{sibling}(X, Y) &\gets \mathsf{parent}(X, Z) \land \mathsf{parent}(Y, Z), \nonumber \\
    \mathsf{father}(X, Y) &\gets \mathsf{parent}(X, Y) \land \neg\mathsf{mother}(X, Y). \label{eq:example_clause}
  \end{align}
  Its predicate dependency graph is in \cref{fig:predicate_dependencies}.
  Because of the negation in \cref{eq:example_clause} (as seen in
  \cref{fig:example_tree2}), the edge from $\mathsf{mother}$ to
  $\mathsf{father}$ is negative, while the other two edges are positive.

@@

Given an undetermined model, we can classify all dependencies of a predicate
$\mathsf{P}$ into three categories based on how many of the edges on the path
from the dependency to $\mathsf{P}$ are undetermined. In the case of zero, we
call the dependency \emph{determined}. In the case of one, we call it
\emph{almost determined}. Otherwise, it is \emph{undetermined}. In the context
of propagation and entailment algorithms, we define a \emph{dependency} as the
sum type:
\begin{grammar}
  <dependency> ::= $\Determined p$ | $\Undetermined p$ | $\AlmostDetermined(p,
  s, t)$
\end{grammar}
where $p \in \predicates{}$ is the name of the predicate which is the
dependency of $\mathsf{P}$, and---in the case of $\AlmostDetermined$---$(s, t)
\in \predicates{}^2$ is the one undetermined edge in $\mathbf{A}$ that prevents
the dependency from being determined. For a dependency $d$---regardless of its
exact type---we will refer to its predicate $p$ as $d.\variable{predicate}$. In
describing the algorithms, we will use an underscore to replace any of $p$, $s$,
$t$ in situations where the name is unimportant.

\begin{algorithm}[p]
  \SetKwFunction{getDependencies}{getDependencies}
  \SetKwFunction{isDetermined}{isDetermined}
  \SetKwFunction{fail}{fail}
  \SetKwFunction{removeValue}{removeValue}
  \SetKwData{predicate}{predicate}
  \SetKwData{source}{source}
  \SetKwData{target}{target}
  \KwData{predicates $p_1$, $p_2$; adjacency matrix $\mathbf{A}$}
  \For{$(d_1, d_2) \in \getDependencies{$p_1$, \logical{false}} \times
      \getDependencies{$p_2$, \logical{false}}$ such that $d_1.\predicate =
      d_2.\predicate$}{
    \lIf{$d_1$ {\bf is} $\Determined$ {\bf and} $d_2$ {\bf is}
      $\Determined$}{\fail{}}
    \If{$d_1$ {\bf is} $\Determined$ {\bf and} $d_2$ {\bf is}
      $\AlmostDetermined(\_, s, t)$ {\bf or} \hspace{50pt} $d_2$ {\bf is} $\Determined$ {\bf
        and} $d_1$ {\bf is} $\AlmostDetermined(\_, s, t)$}{
      $\mathbf{A}[s][t]$.\removeValue{$1$}\;
    }
  }
  \caption{Propagation algorithm for predicate independence}
\end{algorithm}
\begin{algorithm}[p]
  \SetKwFunction{getDependencies}{getDependencies}
  \SetKwFunction{isDetermined}{isDetermined}
  \SetKwData{predicate}{predicate}
  \KwData{predicates $p_1$, $p_2$}
  $D \gets \{ (d_1, d_2) \in \getDependencies{$p_1$, \logical{true}} \times
  \getDependencies{$p_2$, \logical{true}} \mid d_1.\predicate = d_2.\predicate
  \}$\;
  \lIf{$D = \emptyset$}{\Return{\textsc{true}}}
  \lIf{$\exists (\Determined \_, \Determined \_) \in D$}{\Return{\textsc{false}}}
  \Return{\textsc{undefined}}\;
  \caption{Entailment check for predicate independence}
  \label{alg:independence_entailment}
\end{algorithm}
\begin{algorithm}[p]
  \SetKwData{edgeExists}{edgeExists}
  \SetKwData{predicate}{predicate}
  \SetKwData{source}{source}
  \SetKwData{target}{target}
  \SetKwData{all}{allDependencies}
  \SetKwFunction{isDetermined}{isDetermined}
  \SetKwFunction{getDependencies}{getDependencies}
  \SetKwProg{Fn}{Function}{:}{}
  \KwData{a $|\predicates{}| \times |\predicates{}|$ adjacency matrix
    $\mathbf{A}$ with $\{ 0, 1 \}$ as the domain}
  \Fn{\getDependencies{$p$, \all}} {
    $D \gets \{ \Determined p \}$\;
    \While{\logical{true}}{
      $D' \gets \emptyset$\;
      \For{$d \in D$ {\bf and} $q \in \predicates{}$}{
        $\edgeExists \gets \mathbf{A}[q][d.\predicate] = \{ 1 \}$\;
        \uIf{$\edgeExists$ {\bf and} $d$ {\bf is} $\Determined$}{
          $D' \gets D' \cup \{ \Determined q \}$
        }
        \uElseIf{$\edgeExists$ {\bf and} $d$ {\bf is} $\AlmostDetermined(\_, s, t)$}{
          $D' \gets D' \cup \{ \AlmostDetermined(q, s, t) \}$\;
        }
        \uElseIf{$|\mathbf{A}[q][d.\predicate]| > 1$ {\bf and} $d$ {\bf is}
          $\Determined r$}{
          $D' \gets D' \cup \{ \AlmostDetermined(q, q, r) \}$\;
        }
        \ElseIf{$|\mathbf{A}[q][d.\predicate]| > 1$ {\bf and} \all}{
          $D' \gets D' \cup \{ \Undetermined q \}$\;
        }
      }
      \lIf{$D' = D$}{\Return{$D$}}
      $D \gets D'$\;
    }
  }
  \caption{Computing the dependencies of a predicate}
\end{algorithm}
\begin{figure}[t]
  \centering
  \begin{minipage}{.49\textwidth}
    \centering
    \[
      \begin{blockarray}{ccccccc}
        \begin{block}{ccc(cccc)}
          \mathsf{father} & & & 0 & 0 & 0 & 0 \\
          \mathsf{mother} & & & 1 & 0 & 0 & 0 \\
          \mathsf{parent} & & & 1 & \fbox{\{ 0, 1 \}} & \{ 0, 1 \} & \{ 0, 1 \} \\
          \mathsf{sibling} & & & 0 & 0 & 0 & 0 \\
        \end{block}
      \end{blockarray}
    \]
    \caption{The adjacency matrix defined using \cref{def:adjacency_matrix} for
      \cref{example:independence}}
    \label{fig:dependencies_matrix}
  \end{minipage}
  \begin{minipage}{.5\textwidth}
    \centering
    \begin{tikzpicture}
      \node[draw] (parent) at (0, 0.5) {$\mathsf{parent}$};
      \node[draw] (mother) at (0, -0.5) {$\mathsf{mother}$};
      \node[draw] (sibling) at (2, 0.5) {$\mathsf{sibling}$};
      \node[draw] (father) at (2, -0.5) {$\mathsf{father}$};
      \draw[-{Stealth}] (parent) edge (father);
      \draw[-{Stealth}] (mother) edge (father);
      \draw[-{Stealth},dashed,darkgray] (parent) edge (sibling);
      \draw[-{Stealth},dashed,darkgray] (parent) edge (mother);
    \end{tikzpicture}
    \caption{The predicate dependency graph that corresponds to
      \cref{fig:dependencies_matrix}. Dashed edges are undetermined---they may
      or may not exist.}
    \label{fig:dependencies2}
  \end{minipage}
\end{figure}

@@

% TODO: Discuss that the algorithms work in case there are multiple 'paths'
% without any issues.
% TODO: make sure my definitions and examples are consistent with loops

@@

\section{Entailment Checking for Negative Cycles}
% TODO: NB: the set of decision variables for this constraint must exclude all
% arguments.
% TODO: My paper has two slightly different graphs with the same name.

\begin{algorithm}[t]
  \KwData{a constraint model for a logic program $\mathscr{P}$ amid execution}
  \SetKwFunction{hasNegativeCycles}{hasNegativeCycles}
  Let $\mathscr{R} \subseteq \mathscr{P}$ be the largest subprogram of
  $\mathscr{P}$ with all bodies and all predicates in heads fully
  determined\footnotemark\;
  \lIf{$\mathscr{R} = \emptyset$}{\Return{\textsc{undefined}}}
  \lIf{\hasNegativeCycles($G_{\mathscr{R}}$)}{\Return{\textsc{false}}}
  \lIf{$\mathscr{R} = \mathscr{P}$}{\Return{\textsc{true}}}
  \Return{\textsc{undefined}}\;
  \caption{Entailment check for negative cycles}
  \label{alg:negative_cycles}
\end{algorithm}
\footnotetext{Due to the definition of independence, the arguments of the head
  atom need not be determined.}

The \texttt{hasNegativeCycles} function is just a simple extension of the cycle
detection algorithm that `travels' around the graph following edges and
checking if each vertex has already been visited or not.

The difficulty with creating a propagation algorithm for negative cycles is that
there seems to be no good way to extend \cref{def:adjacency_matrix} so that the
adjacency matrix captures positivity/negativity.

\section{Empirical Performance}
% TODO: need a lot more writing

We split the decision variables into the following groups:
\begin{enumerate}
\item all head predicates,
\item for each clause:
  \begin{enumerate}
  \item $\variable{treeStructure}$,
  \item body predicates,
  \item head arguments,
  \item (if $|\variables{}| > 1$) $\variable{introductions}$,
  \item body arguments.
  \end{enumerate}
\end{enumerate}
And use the `fail first' variable ordering heuristic within each group.

We make no claim that this is optimal, but it does avoid major sources of
thrashing.
% Example of thrashing: P(X, a) <- ~P(X, b) contradicts the negative cycle
% constrant. Let's try P(X, a) <- P(X, c) instead (and so on).

%If we're thrashing on the negative cycle constraint, there's not much I can do
%about that.

Value ordering heuristic is random (to make the results random).

We also employ a geometric restart policy, restarting after 10, 20, 40,...
failures (contradictions).
